On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Add indices to point sets
[AMZAE] Formulate the conjecture about infinite rails

\item
$\mathcal{P}=\sqrt{154}/{1} * \{ (\pm 345596160; 0);
(\pm219513840 -15069600);
(\pm260201760; 0);
(\pm225792840; 0);
(\pm213234840; 0);
(\pm153961080; 0);
(\pm144668160; 0
(\pm25116000; 0);
(\pm694026840; 0);
(\pm514710560; 0);
(\pm359116940; 0);
(\pm13423904; 0);
(\pm75682880; 0);
(\pm464143680; 0);
(\pm827069880; 0);
(\pm92144325; 0);
(\pm1195180740; 0);
(\pm1236558752; 0);
(\pm44590560; 0);
(\pm339925740; 0);
(\pm117312468; 0)\}
$
(Figure~\ref{42_symm.png}),

@@

\item
$\mathcal{P}=\sqrt{154}/{1} * \{ (\pm435751680; 0);
(\pm276778320; -19000800);
(\pm328080480; 0);
(\pm284695320; 0);
(\pm268861320; 0);
(\pm194124840; 0);
(\pm182407680; 0);
(\pm31668000; 0);
(\pm1559139296; 0);
(\pm1506967020; 0);
(\pm1042827240; 0);
(\pm875077320; 0);
(\pm648982880; 0);
(\pm585224640; 0);
(\pm452799620; 0);
(\pm95426240; 0);
(\pm16925792; 0);
(\pm116181975; 0);
(\pm428602020; 0);
(\pm56222880; 0);
(\pm769560480; 0);
(\pm626458560; 0);
(\pm130761918; 0)\}
$
(Figure~\ref{46_symm.png}),

@@

\item
$\mathcal{P}=\sqrt{154}/{1} * \{ (\pm10022288640; 0);
( \pm6365901360 ; -437018400);
( \pm7545851040 ; 0);
( \pm6547992360 ; 0);
( \pm6183810360 ; 0);
( \pm4464871320 ; 0);
( \pm4195376640 ; 0);
( \pm728364000 ; 0);
( \pm35860203808 ; 0);
( \pm34660241460 ; 0);
( \pm23985026520 ; 0);
( \pm20126778360 ; 0);
( \pm14926606240 ; 0);
( \pm13460166720 ; 0);
( \pm10414391260 ; 0);
( \pm2194803520 ; 0);
( \pm389293216 ; 0);
( \pm2672185425 ; 0);
( \pm9857846460 ; 0);
( \pm1293126240 ; 0);
( \pm17699891040 ; 0);
( \pm14408546880 ; 0);
( \pm3007524114 ; 0);
( \pm3402061572 ; 0)\}
$
(Figure~\ref{48_symm.png}),

@@

Taking

>>>>

\item
$\mathcal{P_42}=\sqrt{154}/{1} * \{ (\pm 345596160; 0);
(\pm219513840 -15069600);
(\pm260201760; 0);
(\pm225792840; 0);
(\pm213234840; 0);
(\pm153961080; 0);
(\pm144668160; 0
(\pm25116000; 0);
(\pm694026840; 0);
(\pm514710560; 0);
(\pm359116940; 0);
(\pm13423904; 0);
(\pm75682880; 0);
(\pm464143680; 0);
(\pm827069880; 0);
(\pm92144325; 0);
(\pm1195180740; 0);
(\pm1236558752; 0);
(\pm44590560; 0);
(\pm339925740; 0);
(\pm117312468; 0)\}
$
(Figure~\ref{42_symm.png}),

@@

\item
$\mathcal{P_46}=\sqrt{154}/{1} * \{ (\pm435751680; 0);
(\pm276778320; -19000800);
(\pm328080480; 0);
(\pm284695320; 0);
(\pm268861320; 0);
(\pm194124840; 0);
(\pm182407680; 0);
(\pm31668000; 0);
(\pm1559139296; 0);
(\pm1506967020; 0);
(\pm1042827240; 0);
(\pm875077320; 0);
(\pm648982880; 0);
(\pm585224640; 0);
(\pm452799620; 0);
(\pm95426240; 0);
(\pm16925792; 0);
(\pm116181975; 0);
(\pm428602020; 0);
(\pm56222880; 0);
(\pm769560480; 0);
(\pm626458560; 0);
(\pm130761918; 0)\}
$
(Figure~\ref{46_symm.png}),

@@

\item
$\mathcal{P_48}=\sqrt{154}/{1} * \{ (\pm10022288640; 0);
( \pm6365901360 ; -437018400);
( \pm7545851040 ; 0);
( \pm6547992360 ; 0);
( \pm6183810360 ; 0);
( \pm4464871320 ; 0);
( \pm4195376640 ; 0);
( \pm728364000 ; 0);
( \pm35860203808 ; 0);
( \pm34660241460 ; 0);
( \pm23985026520 ; 0);
( \pm20126778360 ; 0);
( \pm14926606240 ; 0);
( \pm13460166720 ; 0);
( \pm10414391260 ; 0);
( \pm2194803520 ; 0);
( \pm389293216 ; 0);
( \pm2672185425 ; 0);
( \pm9857846460 ; 0);
( \pm1293126240 ; 0);
( \pm17699891040 ; 0);
( \pm14408546880 ; 0);
( \pm3007524114 ; 0);
( \pm3402061572 ; 0)\}
$
(Figure~\ref{48_symm.png}),

@@

Taking the examples into consideration,
we can conjecture that there is an infinite set with rational distances
that contains $\mathcal{P_48}$.
(However, it is known that\cite{solymosi2010question}
if a rational set S has infinitely many points on a line or on a circle,
then all but 4 resp. 3 points of S are on the line or on the circle.)
